The Spine of American Legal Practice

### 2016-06-29 article/article.Rmd
Fix citations to legislation

[^30]: For full citations to all of the codes that we used, plus links to electronic versions at the Hathi Trust, Google Books or other sources when available, see Kellen Funk, *American Legislation Project* (2015--): <http://kellenfunk.org/legislation>.

>>>>

[^30]: For full citations to all of the codes that we used, plus links to electronic versions at the Hathi Trust, Google Books or other sources when available, see Kellen Funk, "American Civil Procedure: Law on the Books" (2015--16): <http://kellenfunk.org/civil-procedure/procedure-law/>.
